Concurrent Programming with CXL

### 2020-06-23 book/paper.tex
Added more to CXL machine chapter

A name tag consists of the name of the main method of the process,
along with an optional tag specified in the \texttt{spawn}
\index{spawn statement}
\index{tag}
statement.
The default tag is the first argument to the method.
In Figure~\ref{fig:inc}, the created processes have name tags
\texttt{incrementer/0}, \texttt{incrementer/1}, and \texttt{main/()}.

@@

>>>>

A name tag consists of the name of the main method of the process,
along with an optional tag specified in the \texttt{spawn}
\index{spawn statement}
\index{tag}
statement.
The default tag is the first argument to the method.
A name tag is represented as a dictionary with keys \texttt{.name}
and \texttt{.tag}, but we shall often abbreviate it using the notation
\texttt{name/tag}.
For example, in Figure~\ref{fig:inc}, the created processes have name tags
\texttt{incrementer/0}, \texttt{incrementer/1}, and \texttt{main/()}.

@@

CXL can report a variety of failure types:
\begin{itemize}
\item \texttt{Safety violation}: this means something went wrong with
at least one of the executions of the program that it tried.  This
can include a failing assertion, divide by zero, using an uninitialized
or non-existent variable, dividing a set by an integer, and so on.
CXL will print at trace of the shortest bad execution that it found.
\item \texttt{Infinite loop}: some process ran into an infinite loop
in which it got back to the same state without having accessed any
shared variables.
\item \texttt{Non-terminating States}: CXL found one or more states
from which there does not exist an execution such that all processes
terminate.  CXL will not only print the non-terminating state with
the shortest trace, but also the list of processes that are running
at that state, along with their name tags and program counters.
\item \texttt{Stopped States}: Similar to non-terminating states,
these are states in which some processes are left that cannot
terminate.  Chapter~\ref{ch:synch} will explain what it means for
a process to be stopped.
\end{itemize}
